---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CoQR

<!-- badges: start -->
<!-- badges: end -->

The CoQR package fits a dynamic Co-Quantile Regression in the sense that it semiparametrically models the Value at Risk (VaR), i.e., the $\beta$-quantile of $X_t$ jointly with the $\alpha|\beta$-CoVaR of a series $Y_t$ given $X_t$.

## Installation

You can install the development version of CoQR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TimoDimi/CoQR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(quantmod)
library(tidyr)
library(dplyr)
library(tsibble)
library(CoQR)

# Get data from Yahoo Finance
data_Symbols <- lapply(c("JPM", "^GSPC"), function(x) {
  getSymbols(x,
             from = "2000/01/01",
             to = "2021/12/31",
             periodicity = "daily",
             auto.assign = FALSE) %>%
    data.frame(Date=zoo::index(.), check.names=FALSE) %>%
    rename_all(~stringr::str_replace_all(., paste0(x,"."), ""))
})
names(data_Symbols) <- c("JPM", "SP500")

# Collect data as a tsibble with x and y as column names
data_Assets <- dplyr::bind_rows(data_Symbols, .id = "Asset") %>%
  dplyr::group_by(Asset) %>%
  dplyr::mutate(Date=lubridate::as_date(Date),
         NegReturn= -100*(log(Close) - log(lag(Close)))) %>%
  dplyr::select(Date, Asset, NegReturn) %>%
  stats::na.omit() %>%
  tidyr::pivot_wider(names_from=Asset, values_from=NegReturn) %>%
  dplyr::rename(x=JPM, y=SP500) %>%
  tsibble::as_tsibble(index=Date)


# Fit a CoCAViaR-SAV-fullA model
CoCAViaR_obj <- CoQR(data=data_Assets,
                     model="CoCAViaR_SAV_fullA", 
                     SRM="CoVaR", 
                     beta=0.95, 
                     alpha=0.95)

# Get standard errors and print its summary
summary(CoCAViaR_obj)

# Plot the time series and estimated (in-sample) VaR/CoVaR
plot(CoCAViaR_obj)
```

